Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-19 doc/report/msc-report.tex
report: fixed pagination.
report: fixed data set configuration example.
report: capitalization of headers.
report: conclusion is not needed.
report: tag RC2.
report: fixed Göteborg.
report: added little bit on performance to results.

\noindent SE-412 96 Göteborg

@@

\subsubsection*{Slice and dice}

@@

\subsubsection{Physical storage}

@@

A typical configuration looks like this:

@@

\subsection{Internal Data Interchange}

@@

@@

\section{Conclusion}

Last.fm will use for Zohmg in multiple instances of data analysis, most
prominently in the field of web log analysis.

@@

\subsection*{User mappers}

>>>>

\noindent SE-412 96 G{\"o}teborg

@@

\subsubsection*{Slice and Dice}

@@

\subsubsection{Physical Storage}

@@

Listing 5.1 shows an example data set configuration.

@@

\subsection*{Internal Data Interchange}

@@

Zohmg functionality and performance was tested with two data sets. The first one
being Last.fm's web logs for the entirety of 2006, the second one being scrobble
logs. Both of these data sets are several Gigabytes big and both sets have a
cardinality of millions or more. Zohmg imported managed to import these two data
sets and then serve the aggregates at mouse-click rate.

@@

@@

\subsection*{User Mappers}
